---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# sparkstringr

<!-- badges: start -->
<!-- badges: end -->

The **sparkstringr** package provides a set of functions that allow the use of [stringr](https://github.com/tidyverse/stringr/) functionalities in [Spark](https://spark.apache.org/) DataFrames.

The functions are built on top of [stringr](https://github.com/tidyverse/stringr/) main functions adapted with the help of spark_apply command from [sparklyr](https://github.com/sparklyr/sparklyr) package. 

The functions from [stringr](https://github.com/tidyverse/stringr/) adapted in this package are:

- str_detect
- str_count
- str_sub
- str_extract
- str_match
- str_length
- str_pad
- str_trunc
- str_trim
- str_replace
- str_replace_all (conferir)
- str_to_lower
- str_to_upper
- str_to_title
- str_to_sentence
- str_c
- str_dup
- str_split_fixed
- str_order (conferir)



## Installation

You can install the development version of **sparkstringr** from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("biagoncalves/sparkstringr")
```

## Using sparkstringr

Functions in sparkstringr expect a Spark DataFrame and return a new column (similar to dplyr::mutate) in the same Spark DataFrame with the changes desired. The first arguments in all sparkstringr functions are a Spark DataFrame and a column in the Spark DataFrame that will receive the operations.

All functions in sparkstringr start with `spark_str_` and take `(base, 'column', ...)` as arguments. They work as follows:

- `spark_str_detect(base, column, pattern)` detects the presence of a pattern match in a string:

```{r example, include=FALSE}
# library(sparkstringr)
```

```{r spark_str_detect}
# spark_str_detect(iris_tbl, "Species", 'a')
```


### Incluir restante das funções


You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.


